### 2015-06-26 reports/paper/experiment.tex
update
thesis update

\begin{figure}[h!]
\centering
\includegraphics[width=1.0\textwidth]{error_distribution.eps}
\caption{error distribution in the grid. Arrays are placed at $(-0.5$ m$, 0$ m$)$ and $(0.5$ m$, 0$ m$)$}
\label{fig:error_distribution}
\end{figure}
We also calculated the localization error for each tested point in the grid. Figure~\ref{fig:error_distribution} shows the error distribution inside the grid. The error is below $3$ cm for most areas inside the grid. There is one error spike in the mid-left region and we contribute this to audio source misplacement because the error is fairly low and consistent around that spike.

@@

To show how the volume acts as a color control. A simple experiment is shown in Figure~\ref{fig:show_color}. In this experiment, three stripes are drawn with the same acoustic source but different volume. The color is generated in the Hue-Saturation-Value color space where the Saturation and Value are set to $0.9$ while the hue is controlled by the volume. Figure~\ref{fig:show_color_1_1} shows the first stripe where the volume is set to the maximum and the painted color is in the red range. In fig~\ref{fig:show_color_1_2}, we painted another strip after the volume is decreased by $20$ percent. The painted color changed to the blue range after the volume is decreased. In fig~\ref{fig:show_color_1_3}, we painted a third strip where we further decreased the volume by another $20$ percent. In this final stripe, the color changed to the green range. A video demonstration is available at~\cite{demo:color}.

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=1.0\textwidth]{error_distribution.eps}
\caption{Error distribution in the grid. Arrays are placed at $(-0.5$ m$, 0$ m$)$ and $(0.5$ m$, 0$ m$)$}
\label{fig:error_distribution}
\end{figure}
We also calculated the localization error for each tested point in the grid. Figure~\ref{fig:error_distribution} shows the error distribution inside the grid. The error is below $3$ cm for most areas inside the grid. There is one error spike in the mid-left region and we contribute this to audio source misplacement because the error is fairly low and consistent around that spike.

@@

To show how the volume acts as a color control. A simple experiment is shown in Figure~\ref{fig:show_color}. In this experiment, three stripes are drawn with the same acoustic source but different volume. The color is generated in the Hue-Saturation-Value color space where the Saturation and Value are set to $0.9$ while the hue is controlled by the volume. Figure~\ref{fig:show_color_1_1} shows the first stripe where the volume is set to the maximum and the painted color is in the red to orange range. In fig~\ref{fig:show_color_1_2}, we painted another strip after the volume is decreased by $20$ percent. The painted color changed to the blue to purple range after the volume is decreased. In fig~\ref{fig:show_color_1_3}, we painted a third strip where we further decreased the volume by another $20$ percent. In this final stripe, the color changed to the green to yellow range. A video demonstration is available at~\cite{demo:color}.
